Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-24 krs-survey.tex
Filled section on integration with executive layers

\paragraph{Events}

@@

At the same time, the symbolic model often provides a valuable synthetic view
on the whole state of the robot, furthermore easily understandable by the human
developer (the fact \concept{human1 issitting true} is easier to interpret than
the suite of relative coordinates of each joints of the human skeleton, as
provided by the human tracker, for instance).

>>>>

Conversely, the knowledge management module need a tight integration with the
decision-making processes. As for the integration with sensori-motor
layers, the borders of the KRS can be fuzzy and vary from one architecture to
another: many consider symbolic task planning as an integral role of the KRS,
while other have dedicated extensions for planning, some integrate learning as
an on-the-flight process that is part of the KRS, others as an independent
deliberative process, etc.

The actual integration techniques vary also widely, from language extensions
(like the integration of CRAM~\cite{Beetz2010} with KnowRob) and client-server
architectures, to event-driven models (SHARY and ORO~\cite{Alami2011}). Choices
at this level have notable consequences on the whole design of the upper
control architecture of the robot, in particular regarding its modularity and
the ease of addition of new components.

@@

At the same time, the symbolic model often provides a valuable synthetic view
on the whole state of the robot, furthermore easily understandable by the human
developer (the fact \stmt{human1 isSitting true} is easier to interpret than
the suite of relative coordinates of each joints of the human skeleton, as
provided by the human tracker, for instance).
